Rapid technological progress in white light-emitting diodes \\ and its sources in innovation and technology spillovers

### 2023-01-19 2_SSL_EES/article/article_main.tex
added content to the main document

>>>>

\subsection{Bottom-Up Manufacturing Cost Model}

We address the limitations of data availability for the LED manufacturing cost by conducting bottom-up process-step resolution LED manufacturing cost modelling. In our case, it is enabled by the general availability of historical data on prices of relevant raw materials, components, and manufacturing equipment, and the relative cost data on manufacturing processes, which is occasionally published as part of industry press releases \cite{ledinside2013csp}\cite{seoul2015csp}.

We identified two existing cost models for LED manufacturing in the prior literature. The first is the LED Cosim model developed by the technology consultancy System Plus Consulting \cite{cosim2013} \cite{cosim2019}. Due to prohibitive licensing costs, this model could not be used in our study. The second model is the publicly available 2012 LEDCOM cost model prepared for the U.S. Department of Energy by Stephen Bland  \cite{ledcomv2}. It was set up to capture the manufacturing process for phosphor-converted LEDs of different power levels. However, given the remarkable changes in the performance, cost and architecture of LEDs since 2012, as shown in Figures 1-3, this model cannot fully capture the recent advances in LED technology, necessitating a significant modification to bring it up to date with the current state-of-the-art in LED manufacturing.

Given this situation, we developed our own bottom-up LED manufacturing cost model. The model structure is generally based on the 2012 \textit{LEDCOM} cost model, but we expand it significantly both in scope and in its ability to capture historical trends. The model captures three historical time periods corresponding to different “eras” in LED manufacturing: the early period of the first high-power white LEDs around 2003, the period of accelerating consumer adoption of LED lighting around 2012, and the most recent period around 2020, the year of our main data collection efforts. For each of these three periods, the most prevalent manufacturing equipment was identified through industry periodicals, archived website data from the \textit{Internet Archive}, and expert interviews. Because the architecture of LED chips has changed significantly since the introduction of the first commercial devices in 1996, three different chip architectures were initially considered in the model: classical chips, flip chips, and chip-scale package flip chips. The details of the manufacturing process for each architecture were collected from the scientific literature, textbooks and relevant patents. In addition, two LED life cycle analyses \cite{scholand2012life}\cite{casamayor2018comparative} were used to validate the model structure and extract some of the necessary quantitative model inputs. These studies captured a large number of LED manufacturing process steps and included the details on the use of metals, chemicals and electricity for each manufacturing step.
